Optimal (Multiway) Spatial Joins

### 2024-05-30 msj.tex
yufei

        \item Consider any tuple $\bm{t} \in \J(R'_1, ..., R'_{k-2})$. Let $r' = \gbot(\bm{t})$ and $r^*$ be the top-sliced rectangle of $r'$. Then, we have $\dcross_H(\bm{t})$ $\subseteq \cross_H(r^*)$. Furthermore, if the (horizontal) segments of $\cross_H(r^*)$ are sorted in ascending order of y-coordinate, then $\dcross_H(\bm{t})$ includes a prefix of the sorted order.
    }
\end{lemma}

@@

Then, we will prove that each segment $h \in \cross_H(r^*)$ satisfying that the y-coordinate $h$ is no more than $\ytop(B_{\bm{t}})$ is in $\dcross_H(\bm{t})$. This claim leads to the last sentence of Statement (3). Consider an arbitrary $h\in \cross_H(r^*)$, whose y-coordinate $y_h$ satisfies that $y_h \le \ytop(B_{\bm{t}})$. We will prove that $h$ crosses $r'$ and $B_{\bm{t}}$, and therefore $h \in \dcross_H(\bm{t})$.

@@

First, we prove that $h$ crosses $r'$. It suffices to show that $\xleft(h)  < x_1 \leq x_2 < \xright(h)$ and $y_h \in [y_1, y_2]$. Both conditions are satisfied since $h$ crosses $r^* = [x_1,x_2]\times [y_1, \maxtop(r')]$, and $\maxtop(r')\leq y_2$. Then, we prove that $h$ crosses $B_{\bm{t}}$. It suffices to show that $\xleft(h) < \xleft(B_{\bm{t}}) \le \xright(B_{\bm{t}}) < \xright(h)$ and $y_h \in [y_1, \ytop(B_{\bm{t}})]$.
\begin{itemize}
    \item Since $h$ crosses $r'$, we have $\xleft(h) < x_1 \leq x_2 < \xright(h)$. Since $r' = \gbot(B_{\bm{t}})$, we have the x-range of $B_{\bm{t}}$ is contained in $[x_1,x_2]$. Therefore, $\xleft(h) < \xleft(B_{\bm{t}}) \le \xright(B_{\bm{t}}) < \xright(h)$.
    \item Since $h$ crosses $r^*$, we have $y_h \in [y_1, \maxtop(r')]$. By the definition of $h$, we have $y_h \leq \ytop(B_{\bm{t}})$. Therefore, $y_h \in [y_1, \ytop(B_{\bm{t}})]$.
\end{itemize}

>>>>

        \item Consider any tuple $\bm{t} \in \J(R'_1, ..., R'_{k-2})$. Let $r' = \gbot(\bm{t})$ and $r^*$ be the top-sliced rectangle of $r'$. Then, we have $\dcross_H(\bm{t})$ $\subseteq \cross_H(r^*)$. Furthermore, if the (horizontal) segments of $\cross_H(r^*)$ are sorted in ascending order of their y-coordinates, then $\dcross_H(\bm{t})$ includes a prefix of the sorted order.
    }
\end{lemma}

@@

Next, assuming that the segments of $\cross_H(r^*)$ are sorted in ascending order of their y-coordinates,
we will prove that $\dcross_H(\bm{t})$ includes a prefix of the sorted order. It suffices to establish the following equivalent statement:

@@

\minipg{0.8\linewidth} {
    If a segment $h \in \cross_H(r^*)$ has y-coordinate $y_h \le \ytop(B_{\bm{t}})$, then $h$ must be in $\dcross_H(\bm{t})$.
}

\noindent To prove the above, we must explain why $h$ crosses both $r'$ and $B_{\bm{t}}$.

First, we prove that $h$ crosses $r'$. It suffices to show that $\xleft(h)  < x_1 \leq x_2 < \xright(h)$ and $y_h \in [y_1, y_2]$. Both conditions are satisfied since $h$ crosses $r^* = [x_1,x_2]\times [y_1, \maxtop(r')]$, and $\maxtop(r')\leq y_2$.

Then, we prove that $h$ crosses $B_{\bm{t}}$. It suffices to show that $\xleft(h) < \xleft(B_{\bm{t}}) \le \xright(B_{\bm{t}}) < \xright(h)$ and $y_h \in [y_1, \ytop(B_{\bm{t}})]$.
\begin{itemize}
    \item Since $h$ crosses $r'$, we have $\xleft(h) < x_1 \leq x_2 < \xright(h)$. Since $r' = \gbot(B_{\bm{t}})$, we have the x-range of $B_{\bm{t}}$ is contained in $[x_1,x_2]$. Therefore, $\xleft(h) < \xleft(B_{\bm{t}}) \le \xright(B_{\bm{t}}) < \xright(h)$.
    \item Since $h$ crosses $r^*$, we have $y_h \in [y_1, \maxtop(r')]$. By the definition of $h$, we have $y_h \leq \ytop(B_{\bm{t}})$. Therefore, $y_h \in [y_1, \ytop(B_{\bm{t}})]$.
\end{itemize}
